Automating Verification of MPC Security

### 2023-06-19 popl24/pmf.tex
checkpoint

\section{Probability Mass Functions and Program Distributions}

In order to precisely characterize distributions of secrets and views
in programs we define probability mass functions in a standard manner,
following the formulation in \ref{XXX}. In this formulation, memories
denote conjunctions of variable assignments. Intuitively, given a
program $\prog$ with $\iov(\prog) = S \cup V$ and $\store \in
\mems(\iov(\prog))$, when considering the execution of $\prog$
initialized with secrets $\store_S$, we are fundamentally concerned
with the joint probability of the assignments in $\store_V$
conditioned by the assignments $\store_S$. This is because
probabilistic dependence between honest secrets and corrupt views
\emph{is} information leakage.

@@

\paragraph{Example \ref{example-otp} revisited} For small programs it is
helpful to visualize their basic distributions graphically as their
truth tables, where each row corresponds to an equally likely final
memory for the given program. In Figure \ref{fig-basic-distributions}
we show this for Example \ref{example-otp}. In this truth table we can
see that $\sx{1}{0}$ and $\vx{2}{2}$ are perfectly correlated. But
from the adversarial view, $\sx{1}{0}$ is 1 or 0 with equal
probability given any value of $\vx{0}{0}$. More precisely, for any
$\beta_1,\beta_2$ we have:
\begin{mathpar}
(\progd(\prog_{\ref{example-otp}}))(\{\sx{1}{0} \mapsto \beta_1 \}|\{ \vx{0}{0} \mapsto \beta_2 \}) = .5
\end{mathpar}
Note that this corresponds to \emph{perfect secrecy} as described
in \cite{XXX}.

\paragraph{Example \ref{example-lambda-obliv}(a) revisited} As demonstrated
by Example \ref{example-lambda-obliv} taken from \cite{XXX}, it is possible
to leak information probabilistically through obvservable dependencies
in views. In the basic distribution for Example \ref{example-lambda-obliv}(a)
illustrated in Figure \ref{fig-basic-distributions}, we can see that
the adversarial views $\vx{0}{0}$ and $\vx{0}{1}$ are both 1 in
three different runs of the protocol, and in 2 out of 3 the
honest secret $\sx{1}{0}$ is 1. More precisely:
$$
(\progd(\prog_{\ref{example-lambda-obliv}(a)}))(\{\sx{1}{0} \mapsto 1 \}|\{ \vx{0}{0} \mapsto 1, \vx{0}{1} \mapsto 1 \}) = 2/3
$$
An important point illustrated by this example is that the
probability of values in views, and not just the values themselves,
can release information to the adversary.

>>>>

\section{Probability Mass Functions and Program Distributions}
\label{section-pmf}

In order to precisely characterize distributions of secrets and views
in programs we define probability mass functions in a standard manner,
following the formulation in \ref{barthe2019probabilistic}. In this formulation, memories
denote conjunctions of variable assignments. Intuitively, given a
program $\prog$ with $\iov(\prog) = S \cup V$ and $\store \in
\mems(\iov(\prog))$, when considering the execution of $\prog$
initialized with secrets $\store_S$, we are fundamentally concerned
with the joint probability of the assignments in $\store_V$
conditioned by the assignments $\store_S$. This is because
probabilistic dependence between honest secrets and corrupt views
\emph{is} information leakage.

@@

\paragraph{Example \ref{example-otp} revisited} For small programs it is
helpful to visualize their basic distributions graphically as their
truth tables, where each row corresponds to an equally likely final
memory for the given program. In Figure \ref{fig-basic-distributions}
we show this for Example \ref{example-otp}. In this truth table we can
see that $\sx{1}{0}$ and $\vx{2}{2}$ are perfectly correlated. But
from the adversarial view, $\sx{1}{0}$ is 1 or 0 with equal
probability given any value of $\vx{0}{0}$. More precisely, for any
$\beta_1,\beta_2$ we have:
\begin{mathpar}
(\progd(\prog_{\ref{example-otp}}))(\{\sx{1}{0} \mapsto \beta_1 \}|\{ \vx{0}{0} \mapsto \beta_2 \}) = .5
\end{mathpar}
Note that this corresponds to \emph{perfect secrecy} as described
in \cite{barthe2019probabilistic}.

\paragraph{Example \ref{example-lambda-obliv}(a) revisited} As demonstrated
by Example \ref{example-lambda-obliv} taken from \cite{darais2019language}, it is possible
to leak information probabilistically through obvservable dependencies
in views. In the basic distribution for Example \ref{example-lambda-obliv}(a)
illustrated in Figure \ref{fig-basic-distributions}, we can see that
the adversarial views $\vx{0}{0}$ and $\vx{0}{1}$ are both 1 in
three different runs of the protocol, and in 2 out of 3 the
honest secret $\sx{1}{0}$ is 1. More precisely:
$$
(\progd(\prog_{\ref{example-lambda-obliv}(a)}))(\{\sx{1}{0} \mapsto 1 \}|\{ \vx{0}{0} \mapsto 1, \vx{0}{1} \mapsto 1 \}) = 2/3
$$
An important point illustrated by this example is that the
probability of values in views, and not just the values themselves,
can release information to the adversary.
